Network Cascades

### 2016-08-25 paper/paper.tex
Add Related Work section

>>>>

\section{Related Work}

The mathematical basis for the calculations in section \ref{sec:cascade-condition} about the cascade condition is formed by genrating functions (hence the name $G_0''(1)$ for the condition). Generating functions are a convenient tool to express series of numbers in a concise fashion. Applied to propability distributions, they allow for a convenient examination of that distribution.

An introduction to generating functions can be found in \cite{wilf1994generatingfunctionology} (this version of the book is referenced by Watts in his paper below).

A slightly different and more basic version of the approach to finding an analytical cascade condition is described by Watts and his co-authors in \cite{newman2001random}. They use generating functions to express the degree distribution of arbitrary networks and then analyze for component sizes, average component sizes and the phase transition between going from a largely unconnected network to a network that is mostly one single connected component (the ``giant component'', in terms of the paper). One can easily see, although this is only a very high level description of the paper's contents, that there are striking parallels to this paper about network cascades. They also go a bit further and analyze for the asymptotic form of the cluster size distribution, the number of neighbors and the average path length.
